---
title: "Workflow"
author: "Gesa von Hirschheydt"
date: "2022-10-27"
output: html_document
---

The code in this file will, if run in the given order, reproduce the data, figures, and numbers presented in the publication:

von Hirschheydt, G., Stofer, S., Kéry, M. 2022/2023: “Mixed” occupancy designs: when do additional single-visit data improve the inferences from standard multi-visit models?


# 1. Simulate data & fit occupancy models

Running the code in this section will produce 6 files and place them into the folder `1_Simulate_data_and_fit_occupancy_models`:

 * Case2x150_CovNull.RData
 * Case2x300.RData
 * Case4x150.RData
 * CovOcc.RData
 * CovDet.RData
 * CovBoth.RData


**IMPORTANT:** Each line in the following chunk will take **between 6 and 10 days** to run! We therefore highly recommend that you run the 6 R-files in parallel on different cores using a High Performance Cluster.

```{r SimulateOccupancy}
source('1_Simulate_data_and_fit_occupancy_models/Case2x150_CovNull.R')
source('1_Simulate_data_and_fit_occupancy_models/Case2x300.R')
source('1_Simulate_data_and_fit_occupancy_models/Case4x150.R')
source('1_Simulate_data_and_fit_occupancy_models/CovOcc.R')
source('1_Simulate_data_and_fit_occupancy_models/CovDet.R')
source('1_Simulate_data_and_fit_occupancy_models/CovBoth.R')
```


# 2. Fit linear models to SEs

The following code chunk takes approximately 2 hours to run.

Running the code in this section will produce a single large file (approximately 8.6 GB) and place it into the folder `2_Fit_linear_models_to_SEs`:

 * estimates.RData

Running the code chunk will take approximately 2.5 hours!

```{r LinearModels}
source('2_Fit_linear_models_to_SEs/analysis.R')
```


# Make figures and extract numbers

Running the first code chunk in this section will produce files with the figures used in the main publication and place them into the folder `3_Make_figures_and_extract_numbers`.

Running this code chunk takes roughly 1 minute.

```{r FiguresManuscript}
source('3_Make_figures_and_extract_numbers/figures_and_numbers.R')
```

Running the next code chunk in this section will produce files with the figures presented in the Appendices and place them into the folder `3_Make_figures_and_extract_numbers`.

Running this code chunk takes roughly 1 minute.

```{r FiguresAppendix}
source('3_Make_figures_and_extract_numbers/supplementary_figures.R')
```
